---
title: "Advanced Meta-Analysis Methods in CBAMM"
author: "CBAMM Development Team"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Advanced Meta-Analysis Methods in CBAMM}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(cbamm)
```

# Advanced Meta-Analysis Methods

The CBAMM package now includes cutting-edge meta-analysis techniques:

## 1. Individual Participant Data (IPD) Meta-Analysis

IPD meta-analysis uses raw patient-level data for more precise estimates:

```{r ipd-example, eval=FALSE}
# Simulate IPD data
ipd_data <- simulate_ipd_data(n_studies = 5, n_patients_per_study = 100)

# Perform IPD meta-analysis
result <- ipd_meta_analysis(
  ipd_data = ipd_data,
  outcome = "outcome",
  treatment = "treatment",
  covariates = c("age"),
  method = "one-stage",
  model_type = "random"
)

summary(result)
```

## 2. Diagnostic Test Accuracy Meta-Analysis

Synthesize diagnostic test performance across studies:

```{r diagnostic-example, eval=FALSE}
# Simulate diagnostic data
dta_data <- simulate_dta_data(n_studies = 10)

# Perform diagnostic accuracy meta-analysis
result <- diagnostic_accuracy(
  data = dta_data,
  TP = "TP", FP = "FP", FN = "FN", TN = "TN",
  study_id = "study_id",
  method = "bivariate"
)

summary(result)
```

## 3. Living Systematic Review

Implement sequential meta-analysis with stopping boundaries:

```{r living-example, eval=FALSE}
# Initial studies
initial_data <- simulate_sequential_data(n_studies = 5)

# Create living review
living_ma <- living_systematic_review(
  initial_data = initial_data,
  effect_size = "effect",
  variance = "variance",
  study_id = "study_id",
  method = "sequential",
  boundaries = "obrien-fleming",
  alpha = 0.05,
  power = 0.80
)

# Update with new evidence
new_study <- simulate_sequential_data(n_studies = 1, start_id = 6)
updated_ma <- update_living_review(living_ma, new_study)

summary(updated_ma)
```

## 4. Prediction Intervals

Calculate prediction intervals for future studies:

```{r prediction-example, eval=FALSE}
# After running a meta-analysis
ma_result <- list(effect = 0.5, se = 0.1, k = 10)

# Calculate prediction interval
pred_int <- calculate_prediction_interval(
  ma_result = ma_result,
  tau2 = 0.04,
  level = 0.95
)

print(pred_int$prediction_interval)
```

## 5. Cross-Design Synthesis

Combine RCTs with observational studies:

```{r cross-design-example, eval=FALSE}
# Simulate data
rct_data <- data.frame(
  study = 1:5,
  effect = rnorm(5, 0.5, 0.1),
  variance = runif(5, 0.01, 0.04)
)

obs_data <- data.frame(
  study = 6:10,
  effect = rnorm(5, 0.6, 0.15),
  variance = runif(5, 0.02, 0.06)
)

# Perform cross-design synthesis
result <- cross_design_synthesis(
  rct_data = rct_data,
  obs_data = obs_data,
  bias_model = "additive"
)

print(result$combined)
```

## Unified Interface

Use the `advanced_meta_analysis()` function for any advanced method:

```{r unified-example, eval=FALSE}
# IPD analysis
result <- advanced_meta_analysis(
  data = ipd_data,
  analysis_type = "ipd",
  outcome = "outcome",
  treatment = "treatment"
)

# Diagnostic accuracy
result <- advanced_meta_analysis(
  data = dta_data,
  analysis_type = "diagnostic",
  TP = "TP", FP = "FP", FN = "FN", TN = "TN"
)
```

