---
title: "Complete Plotting Guide for CBAMM"
author: "CBAMM Package"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Complete Plotting Guide for CBAMM}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 10,
  fig.height = 6,
  eval = FALSE
)
```

# Complete Plotting Guide for CBAMM

This guide covers all plotting functions available in the CBAMM package.

## Cumulative Meta-Analysis Plots

```{r cumulative}
library(cbamm)
data(cumulative_example_data)
result <- cumulative_meta_analysis(cumulative_example_data, order_by = "year")

# Dashboard view
create_cumulative_dashboard(result)

# Evidence trajectory
plot_evidence_trajectory(result)

# Stability assessment
plot_stability_assessment(result)

# Forest evolution
plot_forest_evolution(result)
```

## Forest Plot Variations

```{r forest}
# Classic forest plot
forest_plot_classic(data)

# Quality-colored forest plot
forest_plot_quality(data)

# Bubble forest plot
forest_plot_bubble(data)

# Lollipop forest plot
forest_plot_lollipop(data)
```

## Journal-Specific Forest Plots

```{r journal}
# NEJM style
forest_plot_nejm(data)

# Lancet style
forest_plot_lancet(data)

# RevMan style
forest_plot_revman(data)
```

## Funnel Plot Variations

```{r funnel}
# Classic funnel plot
funnel_plot_classic(data)

# Contour-enhanced funnel plot
funnel_plot_contour(data)

# Regression funnel plot
funnel_plot_regression(data)

# Bubble funnel plot
funnel_plot_bubble(data)
```

## Network Meta-Analysis Plots

```{r network}
# Enhanced network plot
plot_network_enhanced(nma_data)

# League table heatmap
plot_league_heatmap(nma_data)
```

## Customizable Plotting

```{r custom}
# Custom forest plot
forest_plot_custom(data, 
                  point_shape = "triangle",
                  point_color = "darkgreen",
                  left_label = "Favors Control",
                  right_label = "Favors Treatment")

# Custom funnel plot
funnel_plot_custom(data,
                  point_shape = "square",
                  add_contours = TRUE,
                  color_by = "study_quality")
```

This comprehensive plotting system makes CBAMM the most advanced meta-analysis visualization package available in R.

