---
title: "CBAMM Case Study: Advanced Evidence Synthesis for PLOS ONE"
author: "Mahmood et al."
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CBAMM Case Study}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(cbamm)
library(ggplot2)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5
)
```

## Introduction

This vignette demonstrates the core features of the `cbamm` package as described in the PLOS ONE submission. We focus on four key pillars:
1. Transportability to target populations.
2. Multiverse analysis for robustness.
3. Component Network Meta-Analysis (CNMA).
4. One-Stage IPD models.

## 1. Transportability and Core Analysis

We simulate a dataset of 15 cardiology RCTs. Our goal is to pool the results but adjust for a target population that is older and has a higher proportion of females than the average study.

```{r transport}
# Simulate data
set.seed(123)
data <- simulate_cbamm_data(n_studies = 15)

# Define target population
target_pop <- list(
  age_mean = 72,
  female_pct = 0.65,
  bmi_mean = 28,
  charlson = 2.5
)

# Run comprehensive analysis
results <- cbamm(data, target_population = target_pop, performance_mode = "fast")

# Print methodological advice
results$advisor_recommendations$methodological
```

## 2. Multiverse Analysis

To ensure our conclusions aren't dependent on specific τ² estimators, we perform a multiverse sweep.

```{r multiverse}
# Results already computed in the main cbamm() call
mv_df <- results$multiverse
head(mv_df)

# Visualize the multiverse
ggplot(mv_df, aes(x = estimate, y = estimator, color = subset)) +
  geom_point(position = position_dodge(width = 0.5)) +
  geom_vline(xintercept = 0.5, linetype = "dashed") +
  theme_minimal() +
  labs(title = "Effect Estimate Multiverse")
```

## 3. Component Network Meta-Analysis

For complex interventions, we decompose treatments into additive components.

```{r cnma}
# Mock data for combination therapy
data_cnma <- data.frame(
  study_id = rep(1:5, each = 2),
  treatment = c("A", "Placebo", "B", "Placebo", "A + B", "A", "A + B", "Placebo", "B", "A"),
  effect = c(0.5, 0, 0.3, 0, 0.8, 0.4, 0.9, 0, 0.4, 0.6),
  se = 0.1
)

result_cnma <- network_meta_analysis(data_cnma, studies="study_id", treatments="treatment",
                                    effect_size="effect", std_error="se",
                                    reference="Placebo", model="component")

# Individual component effects
result_cnma$results$component_effects
```

## 4. One-Stage IPD Models

Finally, we analyze individual participant data using a mixed-effects model.

```{r ipd}
# Simulate IPD for 3 studies
ipd_list <- simulate_ipd_data(n_studies = 3, n_patients = 50)

# Run one-stage random-effects model
result_ipd <- ipd_meta_analysis(ipd_list, method = "one-stage", model_type = "random")

print(result_ipd)
```

## Conclusion

CBAMM provides a unified, robust, and transparent framework for modern evidence synthesis, as verified by our TruthCert reporting protocol.

```{r report, eval=FALSE}
# Generate final TruthCert report
create_cbamm_report(results, filename = "PLOS_ONE_Case_Study.html")
```
